\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\setlist[itemize]{topsep=2pt,itemsep=2pt,leftmargin=1.2em}
\renewcommand{\baselinestretch}{1.1}
\setlength{\parskip}{0.6em}

% Custom section command
\newcommand{\cvsection}[1]{\vspace{0.8em}\noindent\large\textbf{#1}\vspace{0.4em}\\}

\begin{document}

\begin{center}
    {\LARGE \textbf{Joseph Gandy}} \\[6pt]
    Remote Frontend Web Engineer - Derbyshire\\[6pt]
    \href{mailto:joe@gandy.ws}{joe@gandy.ws} \,|\, \href{https://joegandy.co.uk}{joegandy.co.uk} \,|\, \href{https://github.com/JoeGandy}{github.com/JoeGandy} \,|\, \href{https://log.jiy.io}{log.jiy.io}
\end{center}

\cvsection{Profile}
Frontend Web Engineer with 9+ years' experience building and scaling e-commerce and SaaS platforms. Skilled in React, Next.js, TypeScript, Tailwind CSS, and modern frontend tooling. I've worked across the stack, modernised legacy systems, and mentored teams---but I'm also a tinkerer at heart. Whether it's streamlining analytics for millions of users or building out a SaaS app from scratch, I like solving problems and making things that actually work.

\cvsection{Experience}
\noindent\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
\textbf{Senior Web Engineer --- ASOS plc} & Feb 2023 -- Present \\
\end{tabular*}
\begin{itemize}
  \item Modernised analytics with a new datalayer, replacing scattered scripts and giving product and marketing teams reliable reporting.
  \item Integrated a new advertising platform into the ASOS site, working with product managers and ad partners to launch smoothly.
  \item Mentored junior engineers through pair-programming and reviews, helping them ramp up quickly.
\end{itemize}

\noindent\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
\textbf{Web Engineer --- ASOS plc} & May 2021 -- Feb 2023 \\
\end{tabular*}
\begin{itemize}
  \item Built and maintained product page features using React.js with an Express.js backend.
  \item Supported team growth by mentoring newer engineers and sharing best practices.
  \item Partnered closely with designers and product managers to ship features used by millions of customers worldwide.
\end{itemize}

\noindent\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
\textbf{Full-stack Developer --- Slimming World Ltd} & Apr 2018 -- Apr 2021 \\
\end{tabular*}
\begin{itemize}
  \item Built CRM applications with React.js, TypeScript, and .NET Core APIs.
  \item Took on the Scrum Master role within the team, improving sprint planning and delivery flow.
  \item Delivered new features that improved the member experience and streamlined internal workflows.
\end{itemize}

\noindent\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
\textbf{Senior Drupal Developer --- Adaptive Web Ltd} & Jul 2016 -- Apr 2018 \\
\end{tabular*}
\begin{itemize}
  \item Developed headless CMS solutions using Drupal + React.js.
  \item Built an in-house DevOps toolkit with Docker and Fabric, making project setup quicker across the agency.
  \item Helped the team adopt Agile practices, moving towards structured sprint cycles.
\end{itemize}

\noindent\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
\textbf{Drupal Developer --- Adaptive Web Ltd} & Jun 2014 -- Jul 2016 \\
\end{tabular*}
\begin{itemize}
  \item Developed custom Drupal 7 modules for enterprise clients.
  \item First exposure to Agile practices (scrum, sprint planning), learning how teams actually get stuff done.
\end{itemize}

\cvsection{Education}
\textbf{University of Nottingham} --- BSc Computer Science (2:1) \hfill 2013--2016 \\
\textbf{Derby College} --- Software Development Extended Diploma, D*D*D* \hfill 2011--2013

\cvsection{Technical Skills}
\textbf{Frontend:} React, Next.js, TypeScript, Tailwind CSS, Sass/SCSS, GraphQL \\
\textbf{Backend \& APIs:} Node.js, .NET Core, REST APIs, PHP \\
\textbf{DevOps \& Tools:} Docker, Git, CI/CD, Fabric \\
\textbf{Practices:} Agile (Scrum Master), TDD, Pair Programming

\cvsection{Projects \& Portfolio}
\textbf{Lawnsy} --- SaaS app for smart lawn-care scheduling, built with Supabase + Next.js + Tailwind CSS. Designed the data model, authentication systems, and scheduling logic, all deployed via CI/CD. \href{https://lawnsy.io}{lawnsy.io} \\
\textbf{RSMap} --- Auto-generating React/Gatsby map for Old School RuneScape, featuring dungeon routes, monster locators, and region-highlighting. \href{https://rsmap.uk}{rsmap.uk} \\
\textbf{ShareX Custom Upload} --- Self-hosted PHP uploader compatible with ShareX, enabling seamless uploads of text, images, and files. \\
More projects \& code: \href{https://github.com/JoeGandy}{github.com/JoeGandy}

\cvsection{Personal Interests}
Banjo, 3D Printing, Electronics, Cycling, Video games

\end{document}
